---
title: "Stats"
---

##Standard Normal

$$\phi (x) = \frac{e^{-\frac{1}{2}x^2}}{\sqrt{2\pi}}$$

##R code

We can also run **R** code directly in **Rstudio** and incorporate our results into our web page. For example, let's get a sample of ten observations from the distribution above. We can get a sample using the `rnorm()` function in **R**.

```{r}
x <- rnorm(10)
x
# let's see the histogram
hist(x)
mean(x)
```

Notice that it is hard to see that the sample comes from a standard normal distribution. Let's try a larger sample.

```{r, cache=TRUE}
x <- rnorm(100000)
hist(x)
mean(x)
```

...that's more like it.

###Data Analysis

Since we are developing our website in **Rstudio** we can also carryout our data analysis right here. Let's examine the `mtcars` dataset that is comes with **R**. first let's look at the structure of the dataset. [**mtcars documentation**](http://stat.ethz.ch/R-manual/R-devel/library/datasets/html/mtcars.html)

```{r}
data(mtcars)
str(mtcars)
```

From the documentation, we can see that `hp` is for horsepower and `mpg` is for miles per gallon. Let's plot these two.

```{r}
plot(mpg~hp, data = mtcars)
```

It looks as though milage decreases as horsepower increase, which is expected.

```{r}
lm_mpg_hp <- lm(mpg~hp, data = mtcars)
summary(lm_mpg_hp)
```

Let's see how the plot looks with a regression line.

```{r}
plot(mpg~hp, data = mtcars)
abline(lm_mpg_hp)
```

What are the line's coefficients?

```{r}
knitr::kable(as.data.frame(lm_mpg_hp$coefficients))
```

Notice that I can output tables in **R** and convert them into html tables using `knitr::kable()`.
